Explore tumor cell classification with CellAssign

### 2024-07-10 analyses/cell-type-ewings/template_notebooks/cnv-workflow/02-cellassign.Rmd

```{r base paths}
# The current data directory, found within the repository base directory
data_dir <- file.path("..", "..", "data", "current")
sample_dir <- file.path(data_dir, "SCPCP000015", params$sample_id)

# The path to this module
module_base <- file.path("analyses", "cell-type-ewings")
```

>>>>

```{r base paths}
# The path to this module
module_base <- rprojroot::find_root(rprojroot::is_renv_project)

# repo base is two levels up from module 
repository_base <- dirname(dirname(module_base))

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "current")
sample_dir <- file.path(data_dir, "SCPCP000015", params$sample_id)
```
